\chapter{Results}
\label{ch:results}
The preprocessed dataset, contained in the "cleaneddataset.csv" file, was taken from the Kaggle heart disease dataset and used to assess the performance of the Support Vector Machine (SVM) and Random Forest models. There are 302 samples in this collection, and each sample has 14 variables, including clinical characteristics that are used to identify heart disease.
\\
Key performance indicators like as F1 Score, Accuracy, Precision, and Recall were used to evaluate the models. These measurements provide insight into how well the models categorize patients into those with and without cardiac disease. 
\\


\section{Performance Comparison of SVM and Random Forest Models}

\begin{table}[H]
    \centering
    \caption{Performance Metrics of SVM Model}
    \begin{tabular}{|c|c|c|}
    \hline
    \textbf{Metric} & \textbf{Training} & \textbf{Testing} \\ \hline
    Accuracy        & 0.8631            & 0.7705           \\ \hline
    Precision       & 0.8542            & 0.7273           \\ \hline
    Recall          & 0.9111            & 0.8276           \\ \hline
    F1 Score        & 0.8817            & 0.7742           \\ \hline
    \end{tabular}
\end{table}

\begin{table}[H]
    \centering
    \caption{Performance Metrics of Random Forest Model}
    \begin{tabular}{|c|c|c|}
    \hline
    \textbf{Metric} & \textbf{Training} & \textbf{Testing} \\ \hline
    Accuracy        & 0.9129            & 0.8033           \\ \hline
    Precision       & 0.8958            & 0.7429           \\ \hline
    Recall          & 0.9556            & 0.8966           \\ \hline
    F1 Score        & 0.9247            & 0.8125           \\ \hline
    \end{tabular}
\end{table}

\section{Example of a Table in \LaTeX}
Table~\ref{tab:_ex_tab} is an example of a table created using the package \LaTeX  ``booktabs.'' do check the link: \href{https://en.wikibooks.org/wiki/LaTeX/Tables}{wikibooks.org/wiki/LaTeX/Tables} for more details. A table should be clean and readable. Unnecessary horizontal lines and vertical lines in tables make them unreadable and messy. The example in Table~\ref{tab:_ex_tab} uses a minimum number of liens (only necessary ones). Make sure that the top rule and bottom rule (top and bottom horizontal lines) of a table are present. 

\begin{table}[h!]
    \centering
    \caption{Example of a table in \LaTeX}
    \label{tab:_ex_tab}
    \begin{tabular}{llr}     
        \toprule
        \multicolumn{2}{c}{Bike} \\
        \cmidrule(r){1-2}
        Type    &  Color & Price (\pounds) \\
        \midrule
        Electric    & black   & 700   \\
        Hybrid      & blue    & 500   \\
        Road        & blue    & 300   \\
        Mountain    & red     & 300   \\
        Folding     & black   & 500   \\
        \bottomrule
    \end{tabular}
\end{table}

\section{Example of captions style}

\begin{itemize}
    \item The \textbf{caption of a Figure (artwork) goes below} the artwork (Figure/Graphics/illustration). See example artwork in Figure~\ref{fig:chart_a}. 
    \item  The \textbf{caption of a Table goes above} the table. See the example in Table~\ref{tab:_ex_tab}.
    \item  The \textbf{caption of an Algorithm goes above} the algorithm. See the example in Algorithm~\ref{algo:algo_example}.
    \item The \textbf{caption of a Listing goes below} the Listing  (Code snippet). See example listing in Listing~\ref{list:python_code_ex}. 
\end{itemize} 





\section{Summary}
Write a summary of this chapter.



